% This file was converted to LaTeX by Writer2LaTeX ver. 1.4
% see http://writer2latex.sourceforge.net for more info
\documentclass[a4paper]{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{pdftex, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue, pdftitle=, pdfauthor= , pdfsubject=, pdfkeywords=}
% List styles
\newcommand\liststyleWWNumi{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\alph{enumii}}
\renewcommand\theenumiii{\roman{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi)}
\renewcommand\labelenumii{\theenumii)}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
\newcommand\liststyleWWNumii{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\alph{enumii}}
\renewcommand\theenumiii{\roman{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi)}
\renewcommand\labelenumii{\theenumii)}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
% Page layout (geometry)
\setlength\voffset{-1in}
\setlength\hoffset{-1in}
\setlength\topmargin{1in}
\setlength\oddsidemargin{1.25in}
\setlength\textheight{9.6929in}
\setlength\textwidth{5.7681in}
\setlength\footskip{0.0cm}
\setlength\headheight{0cm}
\setlength\headsep{0cm}
% Footnote rule
\setlength{\skip\footins}{0.0469in}
\renewcommand\footnoterule{\vspace*{-0.0071in}\setlength\leftskip{0pt}\setlength\rightskip{0pt plus 1fil}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.0071in}}\vspace*{0.0398in}}
% Pages styles
\makeatletter
\newcommand\ps@Standard{
  \renewcommand\@oddhead{}
  \renewcommand\@evenhead{}
  \renewcommand\@oddfoot{}
  \renewcommand\@evenfoot{}
  \renewcommand\thepage{\arabic{page}}
}
\makeatother
\pagestyle{Standard}
\title{}
\author{ }
\date{2018-12-11}
\begin{document}
\clearpage\setcounter{page}{1}\pagestyle{Standard}

1

a)

The advantages of CG: 

\liststyleWWNumi
\begin{enumerate}
\item It leaves the least amount of ambiguations. Every word is annotated in details and constrained by strict rules so
that there is only one syntactical way to interpret a given text.
\item It can be applied to running sentences instead of specific texts. The performance on new sentences are more
accurate. If the rules are set correctly, the results are more likely to be correct.
\end{enumerate}
b)

\ \ The advantages of CA:

\liststyleWWNumii
\begin{enumerate}
\item The relationship between words and the importance of each word are also annotated. The emphasis or the major
meaning of a sentence is thus displayed.
\item The machine learning process may find possible defects of grammatical rules.
\end{enumerate}
c)

I will choose CG because I do not like ambiguities, except when the text itself is ambiguously written so that even
humans cannot interpret correctly.


\bigskip

2,\ \ They can be used together.

\ \ On the one hand, CG can benefit from assimilating the ML feature by finding out and fixing potential insufficient
grammatical rules set by human annotators. On the other hand, the ML method can benefit from taking CG features by
eliminating possible ambiguities that yield irrational results and by preventing the ML to generate erroneous rules.


\bigskip

3,

A dog jumps over fast barriers.

The dog jumps fast (adv) or the barriers are fast (adj)?

The disambiguator may assign the word \textit{fast} to be an adj since it is located right before a noun (barriers) and
the verb before it is followed by a preposition (over), which may indicate that an adverb is not necessary here.

As for my personal solution to it, first I argue that morphosyntactic ambiguity like this is not a common occurrence;
most sentences will not encounter this problem. Second, whether the word \textit{fast} here functions as adv or adj
does not affect the main information carried by this sentence, so even if the role of \textit{fast} is arbitrarily
determined, the deviation of meaning is not great.

My rule of thumb is to always treat the word right before a noun as an adj when possible.


\bigskip

4,

\ \ Precision:  $\frac{\mathit{TP}} R$\ \  where TP is True Positive and R is the results found

\ \ Recall:  $\frac{\mathit{TP}} P$ \ where TP is True Positive and P is all the positive items

\ \ False Positive: FP / N where FP is all the negative results that are judged to be positive and N is all the negative
items.


\bigskip

\ \ If disambiguators focus on recall and FP, they emphasize on finding as many positive results as possible even when
some of them are not correct; if on precision, they emphasize on making the results as correct as possible, even at the
cost of overlooking some positive ones..


\bigskip

5,

\ \ Iknowtherussianfederationisgood

\ \ I know the Russian Federation is good (n-gram)

\ \ I Know the Russian. Federation is good. (unigram)
\end{document}
